EGGs are adhesive!

### 2025-03-12 calco/main.tex
corollario 4.9

	Let us assume instead that $h_E$, $h_V$, and $h_Q$  are monos. XXXXX
\end{proof}

>>>>

	Let us assume that $h_E$, $h_V$, and $h_Q$  are monos. 
	We can build the witnesses component-wise.
	\parbox{11cm}{It suffices to take the co-kernels of the three arrows, as done 
	for $h_Q$ in the pushout aside. The resulting triple $\mathcal{K}$ is indeed an hypergraph 
	with equivalence, and the components of the arrows 
	$(f_E, f_V, f_Q), (g_E, g_V, g_Q): \mathcal{H\rightrightarrows K}$ 
	are equalised by $h_E$, $h_V$, and $h_Q$, respectively. It is immediate to check that as
	arrows in $\EqHyp$ they are equalised by $(h_E, h_V, h_Q)$.
	} \hfill
	\parbox{2cm}{
	     \xymatrix@R=18pt{
	        Q_\mathcal{G} \ar@{>->}[d]_{h_Q} \ar@{>->}[r]^{h_Q}& Q_\mathcal{H} \ar@{>->}[d]^{g_Q} \\
	        Q_H \ar@{>->}[r]_{f_Q} & Q_\mathcal{{K}}
              }
         }   
\end{proof}
